**Supplementary Information**

### 2020-03-18 submission/supplementary.Rmd
Changed to Mixed and Monospecific.

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Invaded] and \\textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Invaded] and \\textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of macrophytes (\\textit{C. nodosa} [Invaded] and \\textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

@@

# Joining metadata with the number of sequences and OTUs
invisible(Sys.setlocale(locale="en_GB.utf8"))
metadata_nseq_notus <- inner_join(metadata, nseq_notus, by=c("ID"="Group")) %>%
  select(ID, station, date, season, nseq, notus) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  mutate(date=format(date, "%d %B %Y")) %>%
  mutate(date=str_replace(date, "^0", "")) %>%
  arrange(match(station, c("F", "FCyM", "FCaM", "FCa"))) %>%
  mutate(station=str_replace(station, "^F$", "Seawater")) %>%
  mutate(station=str_replace(station, "^FCyM$", "\\\\textit{Cymodocea nodosa} (Invaded)")) %>%
  mutate(station=str_replace(station, "^FCaM$", "\\\\textit{Caulerpa cylindracea} (Invaded)")) %>%
  mutate(station=str_replace(station, "^FCa$", "\\\\textit{Caulerpa cylindracea} (Nonnvaded)")) %>%
  mutate(ID=str_replace(ID, "^23_1$", "23a")) %>%
  mutate(ID=str_replace(ID, "^23_2$", "23b")) %>%
  mutate(nseq=format(nseq, big.mark=","), notus=format(notus, big.mark=","))

>>>>

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Mixed] and \\textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Mixed] and \\textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of macrophytes (\\textit{C. nodosa} [Mixed] and \\textit{C. cylindracea} [Mixed and Monospecific]) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

@@

# Joining metadata with the number of sequences and OTUs
invisible(Sys.setlocale(locale="en_GB.utf8"))
metadata_nseq_notus <- inner_join(metadata, nseq_notus, by=c("ID"="Group")) %>%
  select(ID, station, date, season, nseq, notus) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  mutate(date=format(date, "%d %B %Y")) %>%
  mutate(date=str_replace(date, "^0", "")) %>%
  arrange(match(station, c("F", "FCyM", "FCaM", "FCa"))) %>%
  mutate(station=str_replace(station, "^F$", "Seawater")) %>%
  mutate(station=str_replace(station, "^FCyM$", "\\\\textit{Cymodocea nodosa} (Mixed)")) %>%
  mutate(station=str_replace(station, "^FCaM$", "\\\\textit{Caulerpa cylindracea} (Mixed)")) %>%
  mutate(station=str_replace(station, "^FCa$", "\\\\textit{Caulerpa cylindracea} (Monospecific)")) %>%
  mutate(ID=str_replace(ID, "^23_1$", "23a")) %>%
  mutate(ID=str_replace(ID, "^23_2$", "23b")) %>%
  mutate(nseq=format(nseq, big.mark=","), notus=format(notus, big.mark=","))
